The paper on \Large \bf Blockchain Frontrunning

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] add figure for regular front-running

\subsubsection{Blockchain Participants}
Any regular (miner or non-miner) user can front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions (a.k.a. transaction fees) can increase or decrease how quickly miners will execute them and include them within the blocks they mine. This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks. Once seeing two identical transactions with different transaction fees,  a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.

@@

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine implementation~\cite{libsubmarine}. User generates an Unlock transaction from which the commitment address is retrieved. By funding the commitment address, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the ``Auction'' is over, anyone can call Finalize function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

>>>>

\subsubsection{Blockchain Participants}
Any regular (miner or non-miner) user can front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions (a.k.a. transaction fees) can increase or decrease how quickly miners will execute them and include them within the blocks they mine. This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks. Once seeing two identical transactions with different transaction fees,  a rational miner will prioritize the transaction that pays higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see Figure~\ref{fig:RegularFrontrunning}. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
\caption{The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
\end{figure}

@@

%TODO: figure for miners reordering attack. it should be just two blocks with transaction inside where the second "modified" one has the orders specifically to profit the miner.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the ``Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295
